\chapter{Upgrading SporksIRCD}
\label{Upgrading}

Remember to consult reference.conf and example.conf \textbf{before} any and all
upgrades, especially whilst reading this section.

\section{Upgrading from 1.3 to 1.4}

There have been numerous changes from 1.3 to 1.4. Please adjust your
configuration files accordingly, and take note of any differences in syntax.

\subsection{Module changes}

Some modules have changed, or have been renamed from 1.3 to 1.4:

\begin{itemize}

% Wow, these are FUGLY! Someone should fix this! I can't use LaTeX effectively
% enough yet to make them look better --Elizabeth

\item{\nolinkurl{botmode.so}, \nolinkurl{ip\_cloaking.so}, and
      \nolinkurl{override.so} \\
	These modules have had usm\_ prepended to their names, in line with the
	chm\_* modes (these are USer Modes).
}

\item{\nolinkurl{chm\_censor.so} and \nolinkurl{chm\_censor\_operonly.so} \\
	Censor is now a module, as well as the module to make it oper only.
	Semantics are otherwise the same.
}

\item{\nolinkurl{m\_chgflags.so} \\
	This module has been added to change a user's auth flags (backported
	to 1.3 but unsupported in that version).
}

\item{\nolinkurl{m\_forcequit.so} \\
	This module has been moved to unsupported. See the directions in
	unsupported/ for more information.
}

\item{\nolinkurl{m\_remove.so} \\
	This module exists as a module now for ircd-seven style /remove. Its
	use is discouraged on moral grounds, but is nonetheless supported.
}

\item{\nolinkurl{sno\_channeljoin.so} \\
	This module has been moved out of unsupported and can be used to view
	channel join and part notices.
}

\item{\nolinkurl{m_grant.so} \\
	This is a new built-in (non-extension) module allowing anyone with the
	oper:grant privilege to give anyone else IRC operator status (this was
	backported to 1.3). Note that this operator status is transient and
	will go away after a disconnect.
	There is also a corresponding ungrant command to remove IRC operator
	status from a person. It has no effect on someone who isn't already an
	operator. Integration with services is planned in a future version.
}

\end{itemize}

\subsection{Configuration changes}

Numerous configuration file changes have taken place between 1.3 and 1.4. Note
that 1.3 files \textbf{must} be upgraded to 1.4 format for everything to work
properly.

\begin{itemize}

\item{
	Privset blocks now support an operstring field, which sets the default
	oper string for that class. Note that operstring fields in oper blocks
	will override this.
}

\item{
	Account fields are now supported in oper blocks. This means that the
	user's account name must match the given account name in order to be
	able to oper up.
}

\item{
	caps\_threshold in the channel block has been moved to the blockcaps
	\{\} block as the threshold option. The semantics are otherwise the
	same.
}

\item{
	max\_censors and max\_censors\_large have been moved to the censor \{\}
	block with the same semantics as before.
}

\item{
	expire\_override\_time and make\_override\_immune have been moved to
	the override \{\} block as the expire\_time and make\_immune settings,
	with the same semantics.
}

\item{
	Flood control settings are now configurable.
	client\_flood\_burst\_rate, client\_flood\_burst\_max,
	client\_flood\_message\_time, and client\_flood\_message\_num are all
	configurable settings. The defaults for them are considered sane and
	should not be changed unless you know what you are doing. However,
	client\_flood\_max\_lines may be tweaked and
	does what the old (removed) client\_flood option does.
}

\end{itemize}


\subsection{Miscellaneous}

These are miscellaneous changes you should be aware of, but are not necessarily
major.

\begin{itemize}

\item{
	DES is deprecated and will spew warnings if it is being used for
	passwords. Please upgrade your passwords to a stronger hash function
	(DES is easily cracked on modern machines).
}

\item{
	IPv6 blacklists are now supported via a type parameter (must come
	before the reason). Note not many blacklists support IPv6 yet and thus
	the default is still IPv4.
}

\end{itemize}

